The PAPER-32 power spectrum measured at several redshifts

### 2014-04-30 ms.tex
fixed an unfinished sentence or two in the discussion and fleshed out the conclusions a little bit

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{{figures/pspec_log_z_10.29}.png}
\includegraphics[width=0.45\textwidth]{{figures/pspec_log_z_8.54}.png}
\includegraphics[width=0.45\textwidth]{{figures/pspec_log_z_7.94}.png}
\includegraphics[width=0.45\textwidth]{{figures/pspec_log_z_7.68}.png}
\includegraphics[width=0.45\textwidth]{{figures/pspec_log_z_7.55}.png}
\caption{\label{fig:pspecs} Left to right from top: power spectra centered on redshifts 10.3,8.5, 7.9, 7.7 and 7.6 (frequencies: 127, 149.5, 159.5 164.5, and 167 MHz) at an effective bandwidth of 10MHz or redshift range 0.5  }
\end{figure}
\section{Results}
\label{sec:results}
\subsection{Foreground Filtering and Noise Levels}
\label{sec:noise}
The root-mean-square of the residual measures how well we've removed foregrounds.  In Figure \ref{fig:noise} we examine $T_{rms}$ as calculated by differencing between adjacent channels and between redundant baselines. We see that in the last step of coherent integration, the step between 40 second to 789 second integrations, the noise level decreases by the expected factor of $\sqrt{789/40}$.  At both stages the noise level found by both methods is roughly consistent with the theoretical level, only deviating significantly at the edges where the effective signal to noise due to the Blackman Harris window drops precipitously.

@@

@@

With this paper we have extended the redshift coverage of \cite{Parsons:2013p9876} to cover the range $10.5>z>7.6$.  The amount of foreground contamination slowly increases with redshift, paralleling the level of incoherent noise observed  This highlights the limitation of a the simple Blackman-Harris weighting scheme. Namely that the model of

With only 32 antenna, this data lacks the sensitivity to exclude all but the most extreme models, however, it does demonstrate the ability of the wideband filtration method to affectively remove foregrounds to the precision needed to integrate a full season to the thermal noise limit.  As future observations with PAPER  will add sensitivity primarily by increasing to 128 antennae this projects well for our ability to reach design sensitivity.

>>>>

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{{figures/pspec_log_z_10.29}.png}
\includegraphics[width=0.45\textwidth]{{figures/pspec_log_z_8.54}.png}
\includegraphics[width=0.45\textwidth]{{figures/pspec_log_z_7.94}.png}
\includegraphics[width=0.45\textwidth]{{figures/pspec_log_z_7.68}.png}
\includegraphics[width=0.45\textwidth]{{figures/pspec_log_z_7.55}.png}
\caption{\label{fig:pspecs} Left to right from top: power spectra centered on redshifts 10.3,8.5, 7.9, 7.7 and 7.6 (frequencies: 127, 149.5, 159.5 164.5, and 167 MHz.  All with an effective bandwidth of $\pm$10MHz which covers the redshift span $\Delta z\approx$1421MHz ($B/f^2$) which ranges from 0.8 at $z=$10.3 to 0.45 at $z=$7.4.  }
\end{figure}
\section{Results}
\label{sec:results}
\subsection{Foreground Filtering and Noise Levels}
\label{sec:noise}
The root-mean-square of the residual measures how well we've removed foregrounds.  In Figure \ref{fig:noise} we examine $T_{rms}$ as calculated by differencing between adjacent channels and between redundant baselines. We see that in the last step of coherent integration, the step between 40 second to 789 second integrations, the noise level decreases by the expected factor of $\sqrt{789/40}$.  At both stages the noise level found by both methods is roughly consistent with the theoretical level, only deviating significantly at the edges where the effective signal to noise due to the Blackman Harris window drops precipitously.

@@

%Across the entire band some $k$ modes appear to be dominated somewhat by non-noise systematics, these are not always clearly foregrounds because they appear at only certain $k$ modes rather than clearly emanating from small delays like in the z=10.3 power spectrum.

@@

With this paper we have extended the redshift coverage of \cite{Parsons:2013p9876} to cover the range $10.5>z>7.6$.  The amount of foreground contamination slowly increases with redshift, paralleling the level of incoherent noise observed  This highlights the limitation of the Blackman-Harris weighting scheme used to estimate the broadband foreground model which trades spectral coverage for isolation between delay modes.  Accessing these regions nearer to the edge of the band, where there is less spectral information on which to base a foreground model will require some combination of methods for removing foregrounds that make maximal use of the full band without as much down-weighting, as well as a more precise method for removing foregrounds in the narrow band-power spectrum.

With only 32 antenna, this data lacks the sensitivity to exclude all but the most extreme models, however, it does demonstrate the ability of the wideband filtration method to affectively remove foregrounds to the precision needed to integrate a full season to the thermal noise limit.  As future observations with PAPER  will add sensitivity primarily by increasing to 128 antennae this projects well for our ability to reach design sensitivity.  The residual foregrounds analyzed here are all at or near the level of noise and expose the next level of removal required to access a wider redshift range.
